---
title: "Assignment 5"
Author: Sabikunnahar Shorna
output:
  word_document: default
  pdf_document: default
---


### Creating figures

The assignment is about creating an expository figure from an initial exploratory figure. The data used came from FSAdata package. 

```{r, results = 'hide'}
library(tidyverse)
library(ggplot2)
library(viridis)
library(FSAdata)
```

### FSAdata

```{r include = FALSE}
FSAdata::SiscowetMI2004
```

```{r Data}
head(SiscowetMI2004)
```

### Exploratory Plots

We will explore the data by plotting lengths and weights
```{r}
SiscowetMI2004 %>%
  ggplot(aes(x=len,
             y=wgt)) +
  geom_point()
```

### Expository Plots

We will now create an expository figure. Here, we will also examine the locations with the fishes length and weight.

```{r}
SiscowetMI2004 %>%
  ggplot(aes(x=len,
             y=wgt,
             color=locID)) +
  geom_point() +
  xlab("Total length (mm)") +
  ylab("Weight (g)") +
  labs(title = "Lengths and weights for male and female \n Siscowet Lake Trout captured at four locations \n in Michigan waters of Lake Superior",
       color= "Locations") +
  scale_color_viridis_d() +
  theme_minimal() +
  theme(plot.title.position = "panel",
        axis.title.y = element_text(angle = 90, vjust = .8,size=12),
        axis.text = element_text(size=12),
        legend.position = c(.85, .8)) +
  geom_smooth(method = "lm", se = FALSE)
```